Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-08-08 manuscript/coverletter/collabra_response.tex
had forgotten to describe chou2016 in appendix, fixed

		We have checked that the links in %TODO foobar
		all work, and updated the README to be much more detailed.

		Unfortunately, we don't have a way to edit the individual pre-registrations, but we believe all the necessary information for the rescues is now available.

@@

		 \revised{\begin{verbatim}
		 		### First-replication-reports and Individual-rescue-reports
		 		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
		 		* to view, download the repo and open the html files in a browser

		 	\end{verbatim}}

@@

		\revised{ \begin{verbatim}
			The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
			* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
			* This file uses code/helper/parse_stats.R \end{verbatim}}

		\revised{\begin{verbatim}
				### First-replication-projects and Individual-rescue-projects
			* include the individual replication and rescue projects (aka github repos) respectively
			* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}

>>>>

		We have checked that the links data/combined\_data.csv
		all work, and updated the README to be much more detailed.

		Unfortunately, we don't have a way to edit the individual pre-registrations, but we believe all the necessary information for the rescues is now available, linked from the data sheet.

@@

		% \revised{\begin{verbatim}
		 %		### First-replication-reports and Individual-rescue-reports
		 %		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
		 %		* to view, download the repo and open the html files in a browser

		 %	\end{verbatim}}

@@

	%	\revised{ \begin{verbatim}
	%		The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
	%		* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
	%		* This file uses code/helper/parse_stats.R \end{verbatim}}

	%	\revised{\begin{verbatim}
	%			### First-replication-projects and Individual-rescue-projects
	%		* include the individual replication and rescue projects (aka github repos) respectively
	%		* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}

### 2024-08-08 manuscript/manuscript.Rmd
had forgotten to describe chou2016 in appendix, fixed

>>>>

@chou2016 studied whether a sense of control affects how much one feels physical pain. Participants were asked to recall experiences where they had either a low or high amount of control and then to report their level of physical pain. The first replication closely followed the methods of the original, but added a manipulation check borrowed from a different experiment in @chou2016. The manipulation check was successful, but there were no significant difference in pain level between the two groups. The rescue added pre-survey questions about pain levels to confirm that participants in the two groups had the same baseline understanding of pain. The rescue also did not find a significant difference in pain level between groups.

### 2024-08-08 manuscript/manuscript.tex
had forgotten to describe chou2016 in appendix, fixed

>>>>

Chou et al. (\citeproc{ref-chou2016}{2016}) studied whether a sense of control affects how much one feels physical pain. Participants were asked to recall experiences where they had either a low or high amount of control and then to report their level of physical pain. The first replication closely followed the methods of the original, but added a manipulation check borrowed from a different experiment in Chou et al. (\citeproc{ref-chou2016}{2016}). The manipulation check was successful, but there were no significant difference in pain level between the two groups. The rescue added pre-survey questions about pain levels to confirm that participants in the two groups had the same baseline understanding of pain. The rescue also did not find a significant difference in pain level between groups.
